% Anuj Joshi — 1-page Resume (tight spacing, clear hierarchy)
% Compile with pdfLaTeX.

\documentclass[10pt,a4paper]{article}

% ---- Page ----
\usepackage[a4paper,margin=1.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

% ---- Styling ----
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Thin divider colour
\definecolor{rulegray}{HTML}{D6D6D6}

% ---- Global vertical rhythm ----
\newcommand{\sectionbefore}{8pt}
\newcommand{\sectionafter}{6pt}
\newcommand{\blocksep}{6pt}
\newcommand{\linesep}{3pt}
\newcommand{\headerblocksep}{4pt}
\newcommand{\projectsep}{6pt}

% ---- Section hierarchy (section + section*) ----
\titleformat{name=\section}
  {\bfseries\large}
  {}
  {0pt}
  {}
  [\vspace{2pt}{\color{rulegray}\hrule}]

\titleformat{name=\section,numberless}
  {\bfseries\large}
  {}
  {0pt}
  {}
  [\vspace{2pt}{\color{rulegray}\hrule}]

\titlespacing*{name=\section}{0pt}{\sectionbefore}{\sectionafter}
\titlespacing*{name=\section,numberless}{-pt}{\sectionbefore}{\sectionafter}

% ---- Lists ----
\setlist[itemize]{
  leftmargin=*,
  itemsep=2pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

\newenvironment{jobitems}
  {\begin{itemize}[topsep=1pt]}
  {\end{itemize}}

% ---- Helpers ----
\newcommand{\contactsep}{\;\textbar\;}

\newcommand{\jobheading}[4]{%
  \textbf{#1}\hfill \textbf{#2}\par
  \textit{#3}\hfill \textit{#4}\par
}

\newcommand{\tightlinebreak}{\par\vspace{\linesep}}

\newcommand{\project}[2]{%
  \textbf{#1}\par
  #2\par
}

% Header divider (identical to section headers, colour scoped)
\newcommand{\headerrule}{%
  \vspace{1pt}{\color{rulegray}\hrule}\vspace{\headerblocksep}
}

\begin{document}

% ================= HEADER =================
{\huge \textbf{Anuj Joshi}}\par
\vspace{2pt}
{\large \textbf{Senior Software Engineer \,|\, Full-Stack Developer}}\par
\headerrule
Frankfurt am Main, Germany
\contactsep \href{mailto:joshi.anujo7@gmail.com}{joshi.anujo7@gmail.com}
\contactsep +49 176 4578 2221\par
\href{https://ajoshi.netlify.app/}{ajoshi.netlify.app}
\contactsep \href{https://github.com/joshianuj}{github.com/joshianuj}
\contactsep \href{https://linkedin.com/in/joshianujo7}{linkedin.com/in/joshianujo7}

% ================= SUMMARY =================
\section*{Summary}
Senior Software Engineer with over 10 years of experience delivering enterprise-scale web applications.
Specialised in React and TypeScript front-end engineering, cloud platforms, CI/CD automation, and reliability practices.
A cross-functional collaborator with a strong focus on scalable architecture and operational excellence.

% ================= SKILLS =================
\section*{Technical Skills}
\textbf{Front End:} React, Next.js (App Router), TypeScript (strict), Modern JavaScript, HTML5, CSS3, Accessibility (WCAG), Tailwind CSS\tightlinebreak
\textbf{Back End:} Node.js, REST APIs, OpenAPI, GraphQL (schema-first), PostgreSQL, Python (Django), Ruby on Rails\tightlinebreak
\textbf{Cloud \& DevOps:} Google Cloud, AWS, Docker, Kubernetes, CI/CD (GitHub Actions, CircleCI), Serverless (Cloud Functions)\tightlinebreak
\textbf{Quality \& Architecture:} System design, scalability, TDD, unit and integration testing, observability (New Relic)

% ================= EXPERIENCE =================
\section*{Experience}

\jobheading{Deutsche Bank}{2020 -- Present}{Senior Software Engineer - Trade Finance and Lending}{Frankfurt, Germany}
\begin{jobitems}
  \item Built and maintained enterprise-scale front-end applications using React, TypeScript, and modern JavaScript.
  \item Led cloud modernisation initiatives, including GKE infrastructure setup and OpenShift (OCP 4) migration.
  \item Standardised CI/CD pipelines using GitHub Actions for one-click and scheduled deployments across microservices.
  \item Improved system reliability through New Relic monitoring and integrated Prisma scanning into CI/CD to enhance security.
\end{jobitems}

\vspace{\blocksep}
\jobheading{Candylabs}{2017 -- 2020}{Software Engineer}{Frankfurt, Germany}
\begin{jobitems}
  \item Delivered full-stack web applications using React, Redux, Django, and GraphQL.
  \item Built CI/CD pipelines with CircleCI, Docker, Kubernetes, and Google Cloud Platform.
  \item Developed automation services, including Slack bots, using Firebase, Cloud Functions, and webhook integrations.
  \item Produced analytics dashboards using BigQuery and Google Data Studio.
\end{jobitems}

\vspace{\blocksep}
\jobheading{Leapfrog Technology Inc.}{2014 -- 2016}{Associate Software Engineer $\rightarrow$ Software Engineer}{Kathmandu, Nepal}
\begin{jobitems}
  \item Owned end-to-end delivery across design, development, deployment, and maintenance of production systems.
  \item Developed Ruby on Rails applications and REST APIs, improving code quality through TDD and structured code reviews.
\end{jobitems}

% ================= PROJECTS =================
\section*{Selected Projects}

\project{Real-Time Multiplayer Game (Pew Pew) \hfill \textit{Winner, React Riot Hackathon}}
{Built a real-time multiplayer game with low-latency player synchronisation. \textit{(JavaScript, WebSockets)}}

\vspace{\projectsep}
\project{Data Analytics of Irregular Sensor Data}
{Applied decision-tree classification to frequency-domain sensor data, including feature extraction and predictive modelling. \textit{(Python, NumPy, Pandas, scikit-learn)}}

\vspace{\projectsep}
\project{CNN-Based Finger Detection}
{Developed a real-time camera interface for finger counting using convolutional neural networks. \textit{(Python, PyQt, TensorFlow, OpenCV)}}

% ================= EDUCATION =================

\section*{Education}

\textbf{M.Eng. in Information Technology} \hfill 2016 -- 2018\\
Frankfurt University of Applied Sciences, Frankfurt, Germany\\
\textit{Key Modules:} Distributed Systems \textbar\ Autonomous Intelligent Systems \textbar\
Computational Intelligence \textbar\ Mobile Computing \textbar\ Stochastic Signals \textbar\ Computer Networks

\vspace{4pt}
\textbf{B.E. in Computer Engineering} \hfill 2011 -- 2015\\
Kantipur Engineering College, Tribhuvan University, Kathmandu, Nepal\\
\textit{Key Modules:} Data Structures \& Algorithms \textbar\ Distributed Systems \textbar\
Artificial Intelligence \textbar\ Big Data Systems


\end{document}
